Spatial Analysis: Design-Based vs Model-Based

### 2021-04-15 draft.Rnw
test MRH personal access token.

\begin{enumerate}
  \item Spatial design-based vs spatial model-based: There are no comparisons in the literature between spatial model-based approaches and *spatially balanced* design approaches. These comparisons are typically between spatial model-based approaches and independent or stratified random sample designs. While important to study this behavior, this comparison is no longer fair nor modern. Spatially balanced sampling has exploded in popularity throughout the last decade, and the design-based vs model-based literature needs to reflect this trend.
  \item A ``fair'' comparison: We feel that literature in this area has considered scenarios that are more well-suited for the model-based scenario. For example, if you simulate a Gaussian error with an exponential covariance and then then compare design-based estimates to model-based estimates assuming an exponential covariance, of course the model-based approach will outperform design-based approaches. These types of comparisons in the literature find model-based approaches generally yield more precise variance estimates. A challenge lies in creating a comparison scenario that is reasonable and intuitive. One thing to consider would be exploring the comparison after estimating a misspecified covariance function using model-based approaches. 
  \item Finite AND infinite populations: Literature in the area focuses specifically on finite populations or infinite populations; we want to discuss both, with a focus on finite populations.
  \item Pragmatic Focus: We see papers in this area tend to be fairly technical. We want the focus to be less on mathematical details and more on discussing the pragmatic questions practitioners will be faced with. For example, a thorough discussion of benefits and drawbacks of each method written for practitioners is warranted.
  \item Provide reliable software and code: Much of the current literature presents the ideas but does not provide adequate access to user-friendly software and code. We would clearly explain how to use \texttt{spsurvey} to design and analyze spatial probability samples and \texttt{sptotal} for FBPK. We would make a GitHub repository / package for the paper walking through code used and containing all manuscript-related documents. Because our code for the simulation study would be easily accessible, practitioners would be able to conduct a small simulation study with parameters that reflect their particular context to compare the two approaches.

@@

@@

\texttt{spsurvey} ($>$ 5.0; we are wrapping up a major update now to 5.0) and \texttt{sptotal} ($>$ 0.1.0)

>>>>

\begin{enumerate}
  \item Spatial design-based vs spatial model-based: There are no comparisons in the literature between spatial model-based approaches and \emph{spatially balanced} design approaches. These comparisons are typically between spatial model-based approaches and independent or stratified random sample designs. While important to study this behavior, this comparison is no longer fair nor modern. Spatially balanced sampling has exploded in popularity throughout the last decade, and the design-based vs model-based literature needs to reflect this trend.
  \item A ``fair'' comparison: We feel that literature in this area has considered scenarios that are more well-suited for the model-based scenario. For example, if you simulate a Gaussian error with an exponential covariance and then then compare design-based estimates to model-based estimates assuming an exponential covariance, of course the model-based approach will outperform design-based approaches. These types of comparisons in the literature find model-based approaches generally yield more precise variance estimates. A challenge lies in creating a comparison scenario that is reasonable and intuitive. One thing to consider would be exploring the comparison after estimating a misspecified covariance function using model-based approaches. 
  \item Finite AND infinite populations: Literature in the area focuses specifically on finite populations or infinite populations; we want to discuss both, with a focus on finite populations.
  \item Pragmatic Focus: We see papers in this area tend to be fairly technical. We want the focus to be less on mathematical details and more on discussing the pragmatic questions practitioners will be faced with. For example, a thorough discussion of benefits and drawbacks of each method written for practitioners is warranted.
  \item Provide reliable software and code: Much of the current literature presents the ideas but does not provide adequate access to user-friendly software and code. We would clearly explain how to use \texttt{spsurvey} to design and analyze spatial probability samples and \texttt{sptotal} for FBPK. We would make a GitHub repository / package for the paper walking through code used and containing all manuscript-related documents. Because our code for the simulation study would be easily accessible, practitioners would be able to conduct a small simulation study with parameters that reflect their particular context to compare the two approaches.

@@

Test MH personal access token.

@@

\texttt{spsurvey} ($>=$ 5.0; we are wrapping up a major update now to 5.0) and \texttt{sptotal} ($>=$ 0.1.0)
